---
title: "Homework 6"
author: "Zoey Zhao"
date: "12/4/2021"
output: github_document
---

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
set.seed(1)
```

# Problem 1

### Build a model
Considering baby's birth weight as a outcome might depend on mother's age, smoking status, gestational age, and weight at delivery.

```{r message=FALSE}
birthweight<- 
  read_csv("./data/birthweight.csv")%>%
  mutate(babysex = as.factor(babysex))%>%
  na.omit()

fit1 = lm(bwt ~ momage + smoken + gaweeks + delwt, data = birthweight)
```

```{r}
birthweight %>% 
  modelr::add_residuals(fit1) %>% 
  modelr::add_predictions(fit1)%>%
  ggplot(aes(x = pred, y = resid)) + geom_point() +
  labs(title = "Plot of Model Residuals Against Fitted Values",
       x = "Fitted Values",
       y = "Residuals")
```
### Cross validation
```{r}
fit2 = lm(bwt ~ blength + gaweeks, data = birthweight)

fit3 = lm(bwt ~ blength + bhead + babysex + blength*bhead + bhead*babysex + blength*babysex + blength*babysex*bhead, data = birthweight)
```

```{r}
cv_df =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    fit1  = map(train, ~lm(bwt ~ momage + smoken + gaweeks + delwt, data = .x)),
    fit2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3  = map(train, ~lm(bwt ~ blength + bhead + babysex + blength*bhead + bhead*babysex + blength*babysex + blength*babysex*bhead, data = .x))) %>% 
  mutate(
    rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
    rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
According to the result of cross-validation, the RMSE for the third model (the one using head circumference, length, sex, and all interactions between these) is the smallest, indicating that this model could be better than other two models.

# Problem 2





