---
title: "Homework 6"
author: "Zoey Zhao"
date: "12/4/2021"
output: github_document
---

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
set.seed(1)
```

# Problem 1

### Build a model
Considering baby's birth weight as a outcome might depend on mother's age, baby's length and head circumference.

```{r message=FALSE}
birthweight<- 
  read_csv("./data/birthweight.csv")%>%
  mutate(babysex = as.factor(babysex))%>%
  na.omit()

fit1 <- lm(bwt ~ momage + blength + bhead + blength*bhead +  momage*blength +momage*bhead + momage*blength*bhead, data = birthweight)

fit1%>%
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r}
birthweight %>% 
  modelr::add_residuals(fit1) %>% 
  modelr::add_predictions(fit1)%>%
  ggplot(aes(x = pred, y = resid)) + geom_point() +
  labs(title = "Plot of Model Residuals Against Fitted Values",
       x = "Fitted Values",
       y = "Residuals")
```
### Cross validation
```{r}
fit2 = lm(bwt ~ blength + gaweeks, data = birthweight)

fit3 = lm(bwt ~ blength + bhead + babysex + blength*bhead + bhead*babysex + blength*babysex + blength*babysex*bhead, data = birthweight)
```

```{r}
cv_df =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    fit1  = map(train, ~lm(bwt ~ momage + blength + bhead + blength*bhead +  momage*blength +momage*bhead + momage*blength*bhead, data = .x)),
    fit2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    fit3  = map(train, ~lm(bwt ~ blength + bhead + babysex + blength*bhead + bhead*babysex + blength*babysex + blength*babysex*bhead, data = .x))) %>% 
  mutate(
    rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
    rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
According to the result of cross-validation, the RMSEs for the first and the third model are smaller than the second one, indicating that the second model might not be as good as the first and the third one.

# Problem 2

```{r message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
fit4 <-
  lm(tmax ~ tmin, data = weather_df) 

fit4%>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities.

```{r}
boot_sample <- function(df) {
  sample_frac(df, replace = TRUE)
}

boot_straps = 
  tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
```

```{r}
bootstrap_results <- 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results) 

bootstrap_results%>%
  summarize(
    ci_lower = quantile(adj.r.squared, 0.025), 
    ci_upper = quantile(adj.r.squared, 0.975))
```

```{r}
bootstrap_results %>% 
  ggplot(aes(x = adj.r.squared)) + geom_density() +
  labs(title = "Distribution of Adjusted R-squared",
       x = "Adjusted R-squared")
```

The distribution of adjusted R-squared is approximately normal with a non-obvious tail extending to low values.




```{r}
bootstrap_results2 <- 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)

log_product<-
  bootstrap_results2 %>% 
  select(term, estimate)%>%
  pivot_wider(names_from = term, values_from = estimate)%>%
  unnest()%>%
  janitor::clean_names()%>%
  mutate(log_product = log(intercept*tmin))%>%
  select(log_product)
  
log_product%>%
  summarize(
    ci_lower = quantile(log_product, 0.025), 
    ci_upper = quantile(log_product, 0.975))
```

```{r}
log_product %>% 
  ggplot(aes(x = log_product)) + geom_density() +
  labs(title = "Distribution of Log(Beta0*Beta1)",
       x = "Log(Beta0*Beta1)")
```

The distribution of log(beta0*beta1) is approxiamtely normal.


